\documentclass{exam}

\usepackage[margin=1in]{geometry}

\usepackage{comment}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
%    linkcolor=blue,
%    filecolor=magenta,      
    urlcolor=blue,
    }

\pagestyle{headandfoot}
\firstpageheader{CSCI 221}{}{Logistics Assignment}
\runningheader{CSCI 221}{}{Logistics Assignment}


\begin{document}
\title{Logistics Assignment (Evaluation)}
\author{CSCI 221: Computer Science Fundamentals 2}
\date{Fall 2022}
\maketitle


This assignment is to make sure that everyone has read the syllabus and can access the course resources. 

\textbf{Due Date:}
Friday, September 2nd at 12:00 pm. 

\begin{questions}

\question[5]
\textbf{Syllabus Acknowledgment}

Please read the course syllabus (available on Moodle) and all associated policies. 
When you have done this, please provide a statement that you have read and understood all course policies. 

\question[5]
\textbf{Office Hours}

Please fill out the following whenisgood link: \url{http://whenisgood.net/yj4b8wx} with the times that would work well for you for my office hours. 
Make sure to choose times that work well for you on a weekly basis. 
Please provide a statement that you have done so. 
Additionally, what are your preferences on virtual versus in-person office hours? 
Do you want all virtual? All in-person? Some of each?

\question[5]
\textbf{Course Goals}
What do you hope to get out of this course? 
Please be honest. 
If you are truly taking it just to fulfill a requirement, you can say that, but if there are things you want to learn (on topic), I can try to make sure they are covered. 
\end{questions}

\end{document}